---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nasaR

<!-- badges: start -->
<!-- badges: end -->

The goal of nasaR is to provide useful functions to help access NASA data easily.

## Installation

1. You can install the released version of nasaR from [nasaR](https://github.com/Liu-Zhichao/nasaR) with:

``` r
devtools::install_github("Liu-Zhichao/nasaR")
```

2. You can get your own NASA API token at: [NASA_API](https://api.nasa.gov/). It is highly recommended that you place your private token in the R environment file, and name it "NASA_TOKEN". (the usethis::edit_r_environ() function will be useful). It could help your access to the data be much safer and faster.

## Examples

These are some basic examples which show you how to get access to the data you want:

```{r example_1}
library(nasaR)
## Download an high-definition astronomy picture of 2019/11/01 and return its explanation text as well.
APOD(date = as.Date("2019-11-01"), hd = TRUE, return_text = TRUE)
```

```{r example_2}
## Return info of technology which NASA is working on since 2019/12/01.
Techport(update_since = as.Date("2019-12-01"))
```

## Announcement
R CRAN has an official NASA API interface package called [nasadata](https://cran.r-project.org/web/packages/nasadata/nasadata.pdf). However, the version is quite old and has no longer been updated since 2016, and the functions in this package only take the Earth into consideration, info about other planets/objects in the space are not included in the package. So I decide to make an update(includes all the contents nasadata has and more) and build up various functions for acquiring NASA data easily from available APIs as complete as possible. Find more info about changes/updates in the vignette file.

## Find Out More
You can find lots of useful helper documents in nasaR package. If you don't know meaning of some specific functions, you could check [NASA API official website](https://api.nasa.gov/) for detailed information. I believe that you can find the solution there. If you find any questions or have some interesting new idea of the package, feel free to contact the [author](https://www.linkedin.com/in/zhichao-liu/) directly or leave an issue [here](https://github.com/Liu-Zhichao/nasaR/issues). Thank you!
