---
title: "nasaR"
author: Zhichao Liu
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# devtools::install_github("Liu-Zhichao/nasaR")
library(nasaR)
```

# Functions
The followings show the usage and examples of all functions (sorted alphabetically) included in the package. For detailed meaning of each parameter, please check the helper file of each funtion by running "?[function name]" in the console.  
Tips: All examples are valid only when you place NASA token in R.evironment and name it "NASA_TOKEN" (by default), otherwise you need check the helper file carefully and enter your private key in the function every time.

## APOD
### Description
The function helps print out an stronomy picture of the day. Each day a different image or photograph of our fascinating universe is featured, along with a brief explanation written by a professional astronomer.  

### Parameters
APOD <- function(key = Sys.getenv("NASA_TOKEN"), date = Sys.Date(), hd = FALSE, return_text = FALSE, download_filename = "img.jpg")  

### Examples
```{r, eval=FALSE}
APOD()
APOD(date = as.Date("2019-11-01"), hd = TRUE, return_text = TRUE)
```

## CAD
### Description
This function provides access to current close-approach data for all asteroids and comets in JPL’s SBDB (Small-Body DataBase). See detailed info at: https://ssd-api.jpl.nasa.gov/doc/cad.html. 

### Parameters
CAD <- function(date_min = "now", date_max = lubridate::today() + 60, dist_min = NULL, dist_max = "0.05", h_min = NULL, h_max = NULL, v_inf_min = NULL, v_inf_max = NULL, v_rel_min = NULL, v_rel_max = NULL, class = NULL, pha = FALSE, nea = FALSE, comet = FALSE, nea_comet = FALSE, neo = TRUE, kind = NULL, spk = NULL, des = NULL, body = "Earth", sort = "date", limit = NULL, fullname = FALSE) 

### Examples
```{r, eval=FALSE}
CAD(des = "433", date_min = as.Date("2019-01-01"), date_max = as.Date("2100-01-01"), dist_max = "0.2")
CAD(dist_max = "10LD", date_min = as.Date("2018-01-01"), sort = "dist")
```

## DONKI_CME
### Description
This function provides access to the data of Coronal Mass Ejection (CME).

### Parameters
DONKI_CME <- function(key = Sys.getenv("NASA_TOKEN"), start_date = end_date - 30, end_date = lubridate::today(tzone = "UTC"))

### Examples
```{r, eval=FALSE}
DONKI_CME(end_date = as.Date("2019-11-20"))
```

## DONKI_CME_Analysis
### Description
This function provides access to the data of Coronal Mass Ejection (CME) Analysis.

### Parameters
DONKI_CME_Analysis <- function(key = Sys.getenv("NASA_TOKEN"), start_date = end_date - 30, end_date = lubridate::today(tzone = "UTC"), mostAccurateOnly = TRUE, completeEntryOnly = TRUE, speed = 0, halfAngle = 0, catalog = "ALL", keyword = "NONE")

### Examples
```{r, eval=FALSE}
DONKI_CME_Analysis(start_date = as.Date("2016-09-01"), end_date = as.Date("2016-09-30"), speed = 500, halfAngle = 30)
```

## DONKI_FLR
### Description
This function provides access to the data of Solar Flare (FLR).

### Parameters
DONKI_FLR <- function(key = Sys.getenv("NASA_TOKEN"), start_date = end_date - 30, end_date = lubridate::today(tzone = "UTC"))

### Examples
```{r, eval=FALSE}
DONKI_FLR(start_date = as.Date("2019-01-01"), end_date = as.Date("2019-06-30"))
```

## DONKI_GST
### Description
This function provides access to the data of Geomagnetic Storm (GST).

### Parameters
DONKI_GST <- function(key = Sys.getenv("NASA_TOKEN"), start_date = end_date - 30, end_date = lubridate::today(tzone = "UTC")){

### Examples
```{r, eval=FALSE}
DONKI_GST(start_date = as.Date("2015-01-01"), end_date = as.Date("2015-06-30"))
```

## DONKI_HSS
### Description
This function provides access to the data of Hight Speed Stream (HSS).

### Parameters
DONKI_HSS <- function(key = Sys.getenv("NASA_TOKEN"), start_date = end_date - 30, end_date = lubridate::today(tzone = "UTC"))

### Examples
```{r, eval=FALSE}
DONKI_HSS(start_date = as.Date("2019-01-01"))
```

## DONKI_IPS
### Description
This function provides access to the data of Interplanetary Shock (IPS).

### Parameters
DONKI_IPS <- function(key = Sys.getenv("NASA_TOKEN"), start_date = end_date - 30, end_date = lubridate::today(tzone = "UTC"), location = "ALL", catalog = "ALL")

### Examples
```{r, eval=FALSE}
DONKI_IPS(start_date = as.Date("2019-01-01"), end_date = as.Date("2019-10-31"), location = "Earth")
```

## DONKI_MPC
### Description
This function provides access to the data of Magnetopause Crossing (MPC).

### Parameters
DONKI_MPC <- function(key = Sys.getenv("NASA_TOKEN"), start_date = end_date - 30, end_date = lubridate::today(tzone = "UTC"))

### Examples
```{r, eval=FALSE}
DONKI_MPC(start_date = as.Date("2018-01-01"))
```

## DONKI_Notifications
### Description
This function provides access to the data of Notifications.

### Parameters
DONKI_Notifications <- function(key = Sys.getenv("NASA_TOKEN"), start_date = end_date - 7, end_date = lubridate::today(tzone = "UTC"), type = "all")

### Examples
```{r, eval=FALSE}
DONKI_Notifications(start_date = as.Date("2019-01-01"), end_date = as.Date("2019-03-01"))
```

## DONKI_RBE
### Description
This function provides access to the data of Radiation Belt Enhancement (RBE).

### Parameters
DONKI_RBE <- function(key = Sys.getenv("NASA_TOKEN"), start_date = end_date - 30, end_date = lubridate::today(tzone = "UTC"))

### Examples
```{r, eval=FALSE}
DONKI_RBE(start_date = as.Date("2019-01-01"))
```

## DONKI_SEP
### Description
This function provides access to the data of Solar Energetic Particle (SEP).

### Parameters
DONKI_SEP <- function(key = Sys.getenv("NASA_TOKEN"), start_date = end_date - 30, end_date = lubridate::today(tzone = "UTC"))

### Examples
```{r, eval=FALSE}
DONKI_SEP(start_date = as.Date("2000-01-01"), end_date = as.Date("2010-12-31"))
```

## DONKI_WSAEnlilSimulation
### Description
This function provides access to the data of WSA+EnlilSimulation.

### Parameters
DONKI_WSAEnlilSimulation <- function(key = Sys.getenv("NASA_TOKEN"), start_date = end_date - 7, end_date = lubridate::today(tzone = "UTC"))

### Examples
```{r, eval=FALSE}
DONKI_WSAEnlilSimulation(start_date = as.Date("2019-10-01"), end_date = as.Date("2019-10-15"))
```

## Earth_Assets (This function is similar to "earth_asset" in nasadata package.)
### Description
This function retrieves retrieves the date-times and asset names for available imagery for a supplied location.

### Parameters
Earth_Assets <- function(key = Sys.getenv("NASA_TOKEN"), lat, lon, begin_date, end_date = Sys.Date())

### Examples
```{r, eval=FALSE}
Earth_Assets(lon = 100.75, lat = 1.5, begin_date = as.Date("2014-02-01"))
```

## Earth_Imagery (This function is similar to "earth_image" + "plot_earth_image" in nasadata package.)
### Description
This function retrieves the Landsat 8 image for the supplied location and date.

### Parameters
Earth_Imagery <- function(key = Sys.getenv("NASA_TOKEN"), lat, lon, dim = 0.025, date = Sys.Date(), cloud_score = FALSE, download_filename = "img.png")

### Examples
```{r, eval=FALSE}
Earth_Imagery(lon = 100.75, lat = 1.5, date = as.Date("2014-02-01"), cloud_score = TRUE)
```

## EONET_Events (This function is similar to "earth_event", "eonet_categories", and "eonet_sources" in nasadata package.)
### Description
This function helps get access to the information of events on the Earth (filtered by events/categories/layers).

### Parameters
EONET_Events <- function(source = c("InciWeb", "EO"), status = "open", limit = 5, days = 20, by_events = TRUE, by_layers = FALSE, category_id = 8)

### Examples
```{r, eval=FALSE}
#### Filtered by events:
EONET_Events(source = "InciWeb", limit = 10, days = 30)
#### Filtered by categories:
EONET_Events(category_id = 8, source = "EO", limit = 5, days = 365, by_events = FALSE)
#### Filtered by layers:
EONET_Events(by_layers = TRUE, category_id = 14)
```

## EPIC
### Description
This function helps provide information on the daily imagery collected by DSCOVR's Earth Polychromatic Imaging Camera (EPIC) instrument.

### Parameters
EPIC <- function(key = Sys.getenv("NASA_TOKEN"), query_by_date, date = Sys.Date(), download = FALSE)

### Examples
```{r, eval=FALSE}
EPIC(query_by_date = "natural")
EPIC(query_by_date = "enhanced/date", date = as.Date("2019-11-01"))
EPIC(query_by_date = "natural/date", date = as.Date("2019-06-01"), download = TRUE)
```

## Exoplanet
### Description
This function allows programatic access to NASA's Exoplanet Archive database. See detailed info at: https://exoplanetarchive.ipac.caltech.edu/docs/program_interfaces.html#data.

### Parameters
Exoplanet <- function(table = "exoplanets", select = NULL, count = NULL, colset = NULL, where = NULL,
                      order = NULL, ra = NULL, dec = NULL, radius = NULL, aliastable = NULL)

### Examples
```{r, eval=FALSE}
Exoplanet()
Exoplanet(select = "pl_hostname", order = "dec")
Exoplanet(ra = 291, dec = 48, radius = "1 degree")
Exoplanet(table = "cumulative", where = c("koi_prad<2", "koi_teq>180", "koi_teq<303", "koi_disposition like 'CANDIDATE'"))
Exoplanet(aliastable = "bet Pic")
```

## Fireball
### Description
This function helps provide a method of requesting specific records from the available data-set. Every successful query will return content representing one or more fireball data records. See detailed info at: https://ssd-api.jpl.nasa.gov/doc/fireball.html.

### Parameters
Fireball <- function(date_min = lubridate::today(), date_max = lubridate::today() + 60, energy_min = NULL, energy_max = NULL, impact_e_min = NULL, impact_e_max = NULL, vel_min = NULL, vel_max = NULL, alt_min = NULL, alt_max = NULL, req_loc = FALSE, req_alt = FALSE, req_vel = FALSE, req_vel_comp = FALSE, vel_comp = FALSE, sort = "date", limit = NULL)

### Examples
```{r, eval=FALSE}
Fireball(date_min = as.Date("2014-01-01"), limit = 20)
Fireball(date_min = as.Date("2015-01-01"), req_alt = TRUE, sort = "-date")
```

## GeneLab_Search
### Description
This function helps get access to the data from GeneLab website.

### Parameters
GeneLab_Search <- function(key = Sys.getenv("NASA_TOKEN"), term = "", type = "cgene", from = 0, size = 25, order = "DESC", ffield, fvalue)

### Examples
```{r, eval=FALSE}
GeneLab_Search(term = "space", ffield = "links", fvalue = "GPL16417", type = "cgene,nih_geo_gse")
GeneLab_Search(ffield = "Accession", fvalue = "GSE82255")
```

## Insight
### Description
This function helps provide per-Sol summary data for each of the last seven available Sols (Martian Days).

### Parameters
Insight <- function(key = Sys.getenv("NASA_TOKEN"), ver = "1.0", feedtype = "json", simplified_data_frame = FALSE)

### Examples
```{r, eval=FALSE}
Insight()
Insight(simplified_data_frame = TRUE)
```

## Mission_Design
### Description
This function helps get access to the JPL/SSD small-body mission design suite. See detailed info at: https://ssd-api.jpl.nasa.gov/doc/mdesign.html.

### Parameters
Mission_Design <- function(mode = "Q", des = NULL, spk = NULL, sstr = NULL, class = FALSE, mjd0 = NULL, span = NULL, tof_min = NULL, tof_max = NULL, step = NULL)

### Examples
```{r, eval=FALSE}
#### Mode: Q
Mission_Design(des = "2012%20TC4")
Mission_Design(des = 1, class = TRUE)
Mission_Design(sstr = "apophis")
#### Mode: M
Mission_Design(mode = "M", des = "2012%20TC4", mjd0 = 58490, span = 3652, tof_min = 10, tof_max = 365, step = 2)
```

## MRP_date
### Description
This function helps get access to Mars Rover Photos - Querying by Earth date.

### Parameters
MRP_date <- function(key = Sys.getenv("NASA_TOKEN"), earth_date, camera = "all", page = 1, type = "curiosity", download_image = FALSE)

### Examples
```{r, eval=FALSE}
MRP_date(earth_date = "2015-06-03")
MRP_date(earth_date = "2019-05-01", download_image = TRUE)
```

## MRP_sol
### Description
This function helps get access to Mars Rover Photos - Querying by Martian sol.

### Parameters
MRP_sol <- function(key = Sys.getenv("NASA_TOKEN"), sol = 1000, camera = "all", page = 1, type = "curiosity", download_image = FALSE)

### Examples
```{r, eval=FALSE}
MRP_sol(download_image = TRUE)
MRP_sol(camera = "MAST", page = 2)
MRP_sol(type = "opportunity")
```

## NASA_Image_Video
### Description
This function helps get access to Info of images/videos in NASA Image and Video Library.

### Parameters
NASA_Image_Video <- function(endpoint, nasa_id = NULL, q = NULL, center = NULL, description = NULL, description_508 = NULL, keywords = NULL, location = NULL, media_type = NULL, page = NULL, photographer = NULL, secondary_creator = NULL, title = NULL, year_start = NULL, year_end = NULL)

### Examples
```{r, eval=FALSE}
NASA_Image_Video(endpoint = "search", q = "apollo%2011", description = "moon%20landing", media_type = "image")
NASA_Image_Video(endpoint = "asset", nasa_id = "as11-40-5874")
NASA_Image_Video(endpoint = "metadata", nasa_id = "as11-40-5874")
NASA_Image_Video(endpoint = "captions", nasa_id = "172_ISS-Slosh")
```

## Neo_Browse
### Description
This function helps browse the overall Asteroid dataset.

### Parameters
Neo_Browse <- function(key = Sys.getenv("NASA_TOKEN"))

### Examples
```{r, eval=FALSE}
Neo_Browse()
```

## Neo_Feed
### Description
This function retrieves a list of Asteroids based on their closest approach date to Earth.

### Parameters
Neo_Feed <- function(key = Sys.getenv("NASA_TOKEN"), start_date, end_date = start_date + 7, as_dataframe = FALSE)

### Examples
```{r, eval=FALSE}
Neo_Feed(start_date = as.Date("2019-11-01"), end_date = as.Date("2019-11-03"), as_dataframe = TRUE)
```

## Neo_Lookup
### Description
This function helps lookup a specific Asteroid based on its NASA JPL small body (SPK-ID) ID.

### Parameters
Neo_Lookup <- function(key = Sys.getenv("NASA_TOKEN"), asteroid_id)

### Examples
```{r, eval=FALSE}
Neo_Lookup(asteroid_id = 3542519)
```

## NHATS
### Description
This function provides a method of requesting data from the NHATS-related tables in the SBDB. See detailed info at: https://ssd-api.jpl.nasa.gov/doc/nhats.html.

### Parameters
NHATS <- function(mode = "S", dv = 12, dur = 450, stay = 8, launch = "2020-2045", h = NULL, occ = NULL, spk = NULL, des = NULL, plot = FALSE)

### Examples
```{r, eval=FALSE}
#### Mode: S
NHATS(dv = 6, dur = 360, stay = 8, launch = "2020-2045", h = 26, occ = 7)
#### Mode: O
NHATS(mode = "O", des = "99942")
NHATS(mode = "O", des = "2000%20SG344", dv = 6, dur = 360, stay = 8, launch = "2020-2045")
```

## Patents - THIS IS DOWN CURRENTLY!
### Description
This function helps get access to the data of NASA's patents.

### Parameters
Patents <- function(key = Sys.getenv("NASA_TOKEN"), query, concept_tags = FALSE, limit = 5)

### Examples
```{r, eval=FALSE}
Patents(query = "temperature")
```

## Scout
### Description
This function provides access to near-realtime results from the CNEOS Scout system. See detailed info at: https://ssd-api.jpl.nasa.gov/doc/scout.html.

### Parameters
Scout <- function(mode = "O", tdes = NULL, plot = NULL, file = NULL, orbits = FALSE, n_orbits = 1000, eph_start = "now", eph_stop = NULL, eph_step = NULL, obs_code = "500", fov_diam = NULL, fov_ra = NULL, fov_dec = NULL, fov_vmag = NULL)

### Examples
```{r, eval=FALSE}
## Note that the NEOCP object tdes used in the following examples is not guaranteed to still exist in the database.
#### Mode: O
Scout(tdes = "P10vY9r")
Scout(tdes = "P10vY9r", plot = "el")
Scout(tdes = "P10vY9r", orbits = 1)
#### Mode: E
Scout(mode = "E", tdes = "P10vY9r", eph_start = "2016-09-24T12:00:00")
Scout(mode = "E", tdes = "P10vY9r", eph_start = "2016-09-25T18:00:00", eph_stop = "2016-09-26T06:00:00", eph_step = "2h")
```

## Sentry
### Description
This function provides access to results from the CNEOS Sentry system. See detailed info at: https://ssd-api.jpl.nasa.gov/doc/sentry.html.

### Parameters
Sentry <- function(mode = "S", spk = NULL, des = NULL, h_max = NULL, ps_min = NULL, ip_min = NULL, days = NULL, all = FALSE, removed = FALSE)

### Examples
```{r, eval=FALSE}
#### Mode: O
Sentry(mode = "O", des = "99942")
Sentry(mode = "O", des = "2000%20SG344")
#### Mode: S
Sentry()
#### Mode: V
Sentry(mode = "V", all = TRUE, ip_min = 1e-3)
#### Mode: R
Sentry(mode = "R", removed = TRUE)
```

## Techport
### Description
This function helps discover the technologies NASA is working on every day to explore space, understand the universe, and improve aeronautics.

### Parameters
Techport <- function(key = Sys.getenv("NASA_TOKEN"), id_parameter = NULL, all_valid_id = FALSE, update_since = NULL)

### Examples
```{r, eval=FALSE}
Techport(id_parameter = 17792)
Techport(all_valid_id = TRUE)
Techport(update_since = as.Date("2016-01-01"))
```

## TLE
### Description
This function helps get access to the data of earth-orbiting objects

### Parameters
TLE <- function(satellite_name = NULL, satellite_num = NULL)

### Examples
```{r, eval=FALSE}
TLE(satellite_name = "HTV")
TLE(satellite_num = 43553)
```



